Check Coverage

### 2020-06-17 analysis/merge_data.Rmd
add BAT function for calculating metrics

First pass at calculating FD metrics
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

>>>>

First pass at calculating FD metrics from FD package:
```{r}
data <- biotime_traits %>% 
  filter(!is.na(plot), !is.na(scientificName)) %>% #remove unlabeled plots and observations without traits
  group_by(study_id, year, plot) %>%
  filter(n_distinct(id) > 4) %>%
  ungroup() %>%
  filter(!study_id %in% c(195, 360), #exclude because they break
         !study_id %in% c(217, 327)) #exclude to get the file size smaller

@@

Let's also do the functions from BAT package
```{r}
#function for getting PCA axes with at least 95% coverage
axes95 <- function(mat){
  axes <- pco(mat)
  eigen <- axes$eig

  threshold <- sum(eigen[eigen > 0]) * 0.95

  sums <- cumsum(eigen)
  num_axes <- Position(function(x) x > threshold, sums)

  return(num_axes)
}

get_BAT_fd <- function(data, study, plot_num){
  require(BAT)

  data <- data %>%
    na.omit(id) %>%
    filter(study_id == study, plot == plot_num)

  #get PCA trait matrix
  trait_dist <- gower.dist(trait_mat)
  trait_pco <- pco(trait_dist, k = axes95(trait_dist))

  return(rownames(trait_pco$points) <- rownames)
  # fs::dir_create(paste0(here::here("data"), "/fd_output"))
  # 
  # #the convexhull c code creates an output file of vertices, in order to not have multiple threads writing
  # #to the same file we have to create individual working directories
  # tmp_dir <- paste0(here::here("data", "fd_output", "tmp"), "/tmp_", study, plot_num)
  # fs::dir_create(tmp_dir)
  # setwd(tmp_dir)
  # 
  # fd_out <- as_tibble(dbFD_joggle(trait_mat, species_mat, w.abun = FALSE))[,1:8] %>%
  #   cbind(years, .) %>%
  #   mutate(study_id = unlist(study), plot = unlist(plot_num), trait_count = dim(trait_mat)[2]) %>%
  #   write_tsv(paste0(here::here("data"), "/fd_output/", "s", study, "_p", plot_num, "_fd.tsv"))
  # 
  # setwd(here::here())
  # return(fd_out)
}

```
